Using Scipion for Stream Image Processing at Cryo-EM Facilities

### 2018-10-01 Review/answer_referee.tex

\begin{reviewer}
\section*{Reviewer 1}
\point{The graphical abstract is likely too detailed 
and would not show well when reduced to the image size that the final version has.}

\reply  Both reviewers complain that the graphical abstract need to be redesigned. The first reviewer complains that is ``...too detailed...'' while the second one claims that ``...is oversimplified...''. Since the graphical abstract is not compulsory  and both reviewers dislike it for completely opposite and irreconcilable reasons we have decided to drop it.

\point{The manuscript would benefit from a figure that outlines the layout of a typical Scipion system, showing computers, data connections, data flows in workflow scenarios, and how streaming is now implemented. At least for one of the three examples described, a figure would be helpful and make the manuscript more appealing to readers. }

\reply The following two figures have been included in the manuscript.

@@

\begin{figure}
  \centering
      \includegraphics[width=0.75\textwidth]{images/diagram.pdf}
  \caption{Graphical representation of the data flow through the CNB facility. Green, blue and red lines represent the microscope private network, the \cnb local area network and the public network respectively.}
  \label{fig:cnbpipeline}

\end{figure}
\begin{figure}
%\hspace*{-2cm}                                                           
\includegraphics[width=1.0\textwidth]{images/scilifelab.png}
  \caption{Overview of the Session Wizard  developed at \scilifelab. A) The user triggers the wizard for any of the current microscopes. B) The wizard retrieves project information from the \textit{Application Portal} and reservation details from the \textit{Booking System}. C) The wizard creates data folders, executes the image copying script, configures the Scipion streaming project and logs the current session into a database. D) The \scipion project is used to generate on the fly web reports and invoice documents later on.}
  \label{fig:wizard}

@@

\point{The graphical abstract is oversimplified and does not convey any of the useful information presented in the manuscript. The background is distracting, the cartoons are redundant with the labels, and the image describing the reporting feature is not legible and improperly sized (laterally stretched).}

\reply See answer to reviewer 1 question 1.

\point{Finally, the manuscript could benefit greatly from more visual summaries and schematics to guide the readers especially the non-experts that the authors refer to as part of their target consumer base.}

\reply We think the reviewer refer here to section 4. As commented previously this section has been extensively rewritten to take into account the reviewers' suggestions and it includes a two new figures.

### 2018-10-01 Review/3.workflow_scilifelab.tex
to class

The Swedish National Cryo-EM Facility %%offers access to state-of-the-art equipment and expertise in single particle cryo-EM and cryo electron tomography (cryo-ET). The Facility 
has two nodes: at \scilifelab in Stockholm and at Ume\aa\ University. \scilifelab in Stockholm offers single-particle service with a 
Talos Arctica for sample optimisation and a Titan Krios for high-resolution data collection. The Ume\aa\ node is expected to become operational during 2018, and will offer cryo-ET with a Titan Krios and a Scios DualBeam SEM.
%The facilities can be accessed by Swedish researchers through 
%a peer-reviewed process. Applications can be submitted through an application portal (\url{https://cryoem.scilifelab.se/}). % and will be evaluated once every three months based on their scientific merit and technical feasibility by a national Project Evaluation Committee. %On the other side, some time of the facility is reserved for internal research groups at Stockholm University. 
Internally, an online booking system called \emph{Booked Scheduler} centralizes the reservations of the microscopes and other instruments.

@@

\subsubsection{Additional Software Developments: \emph{Session Wizard}}
In order to interface \scipion with the microscope infrastructure, an upgraded version of the original script developed at CNB was used. Unfortunately, it was difficult to reuse the existing code due to a different folder structure and, more important, a different approach to user and microscope management. To address the new set of requirements, a new wizard has been development at \scilifelab. %(In this contest wizard refers to a helper script which guide users through a certain process.) %For this new wizard, a basic data model was designed representing the current processing and data organization at \scilifelab. %The model is composed by the following entities:

>>>>

The Swedish National Cryo-EM Facility %%offers access to state-of-the-art equipment and expertise in single particle cryo-EM and cryo electron tomography (cryo-ET). The Facility 
has two nodes: at \scilifelab in Stockholm and at Ume\aa\ University. \scilifelab in Stockholm offers single-particle service with a 
Talos Arctica for sample optimisation and a Titan Krios for high-resolution data collection. The Ume\aa\ node offers cryo-ET with a Titan Krios and a Scios DualBeam SEM.
%The facilities can be accessed by Swedish researchers through 
%a peer-reviewed process. Applications can be submitted through an application portal (\url{https://cryoem.scilifelab.se/}). % and will be evaluated once every three months based on their scientific merit and technical feasibility by a national Project Evaluation Committee. %On the other side, some time of the facility is reserved for internal research groups at Stockholm University. 
Internally, an online booking system called \emph{Booked Scheduler} centralizes the reservations of the microscopes and other instruments.

@@

\subsubsection{Additional Software Developments: \emph{Session Wizard}}
In order to interface \scipion with the microscope infrastructure, an upgraded version of the original script developed at CNB was used. Unfortunately, it was difficult to reuse the existing code due to a different folder structure and, more important, a different approach to user and microscope management. To address the new set of requirements, a new wizard has been developed at \scilifelab (see \ffigure{fig:wizard}). %(In this contest wizard refers to a helper script which guide users through a certain process.) %For this new wizard, a basic data model was designed representing the current processing and data organization at \scilifelab. %The model is composed by the following entities:
\begin{figure}
\hspace*{-2cm}                                                           
\includegraphics[width=1.25\textwidth]{images/scilifelab.pdf}
  \caption{Overview of the Session Wizard  developed at \scilifelab. A) The user triggers the wizard for any of the current microscopes. B) The wizard retrieves project information from the \textit{Application Portal} and reservation details from the \textit{Booking System}. C) The wizard creates data folders, executes the image copying script, configures the Scipion streaming project and logs the current session into a database. D) The \scipion project is used to generate on the fly web reports and invoice documents later on.}
  \label{fig:wizard}

\end{figure}
